\section{Secondary input parameters 辅助输入参数}

\begin{Parallel}{0.60\textwidth}{}
    \ParallelLText
    {
        A possible reason for the significant data scatter around the mean trend is that additional explanatory variables are not incorporated into the transformation model. As a result, the variation in these hidden explanatory variables, which is inevitable in a database, is added to the transformation uncertainty. A good example is the $\rm{OCR}-(s_u/\sigma_v')$ model by \citet{Jamiolkowski198557}. The COV with respect to the global database is 0.53 for this model (see Table \ref{table:5}). This means that the standard deviation of the data scatter is about 53$\%$ of the mean trend. A possible hidden explanatory variable is the sensitivity $S_t$ — it is known that the “stress history and normalized soil engineering properties” SHANSEP parameters for sensitive (structured) clays are different from those for insensitive clays. In fact, by incorporating $S_t$ as a secondary input parameter, the $\rm{OCR}-(s_u/\sigma_v')-S_t$ model by \cite{Ching2012522}carries a significantly smaller COV of 0.34 (see Table \ref{table:5}). It is widely known that parameters such as PI and $S_t$ can be applied as secondary explanatory variables for some correlations. It is of interest to see whether the incorporation of these secondary input parameters can reduce COV significantly. If the COV reduction is significant, it is of interest to re-calibrate the transformation models to further update the bias factors and the COVs in Table \ref{table:5}. This is the main objective of this section.
    }
    \ParallelRText
    {
        围绕平均趋势出现大量数据分散的可能原因是，其他解释变量未合并到转换模型中。结果，这些隐藏的解释变量的变化（这在数据库中是不可避免的）被添加到变换不确定性中。一个很好的例子是\citet{Jamiolkowski198557}的$\rm{OCR}-(s_u/\sigma_v')$模型。对于此模型，相对于全局数据库的COV为0.53（请参见表\ref{table:5}）。这意味着数据散布的标准偏差约为平均趋势的53$\%$。可能的隐藏解释变量是敏感度$S_t$ - 已知敏感（结构化）黏土的“应力历史和规范化的土壤工程特性” SHANSEP参数与不敏感黏土的参数不同。实际上，通过将$S_t$作为次要输入参数，\cite{Ching2012522}的$\rm{OCR}-(s_u/\sigma_v')-S_t$模型携带的COV值要小得多，为0.34（参见表\ref{table:5}）。众所周知，诸如PI和$S_t$之类的参数可以用作某些相关性的次要解释变量。有趣的是，这些辅助输入参数的合并是否可以显着降低COV。如果COV降低很大，则需要重新校准转换模型以进一步更新表\ref{table:5}中的偏置因子和COV。这是本节的主要目标。
    }
\end{Parallel}


\Paragraph{Correlation between $\epsilon$ and $(\rm{PI}, S_t)$ $\epsilon$与$(\rm{PI}, S_t)$之间的相关性}

\begin{Parallel}{0.60\textwidth}{}
    \ParallelLText
    {
        Let us recall from eq. (\ref{equal:1}) that the variability term $\epsilon$ for a  transformation model can be expressed as
    }
    \ParallelRText
    {
        让我们从等式(\ref{equal:1})回忆，转换模型的可变性项$\epsilon$可以表示为
    }
    \ParallelPar
    \begin{align}
        \epsilon=\dfrac{\rm{actual~target~value}}{b\times{}\rm{predicted~target~value}}=\dfrac{\rm{actual~target~value}}{\rm{unbiased~prediction}}
        \label{equal:2}
    \end{align}
    \ParallelLText
    {
        where the unbiased prediction = $b\times$ predicted target value. The variability term epsilou quantifies the deviation between the actual value and the unbiased prediction. It has mean value of 1 and COV equal to the calibrated COV (delta). Equivalently
    }
    \ParallelRText
    {
        其中无偏预测 = $b\times$预测目标值。 可变性项$\varepsilon$量化了实际值和无偏预测之间的偏差。它的平均值为1，且COV等于校准的COV（$\delta$）。等效地，
    }
    \ParallelPar
    \begin{align}
        \ln(\varepsilon)=\ln(\rm{actual~target~value})-\ln({\rm{unbiased~prediction}})
        \label{equal:3}
    \end{align}
    \ParallelLText
    {
        In essence, $\ln(\varepsilon)$ is the component that cannot be explained away by the primary input parameter. More precisely, $\ln(\varepsilon)$ should be uncorrelated to the primary input parameter. The reason why the natural logarithm is taken will be explained later. For instance, $\ln(\varepsilon)$ for the $\rm{OCR}-(s_u/\sigma_v')$ model proposed by \citet{Jamiolkowski198557} is indeed nearly uncorrelated to the primary input parameter $\ln(\rm{OCR})$, shown in Fig. \ref{figure:16}a. Incidentally, the correlation between $\ln(\varepsilon)$ and $\ln(\rm{PI})$ is also nearly zero (Fig. \ref{figure:16}b). However, $\ln(\varepsilon)$ and $\ln(S_t)$ show some slight positive correlation (Fig. \ref{figure:16}c). In this case, it may be possible to adopt St as the secondary input parameter for Jamiolkowski et al.’s model to reduce its COV.
    }
    \ParallelRText
    {
        本质上，$\ln(\varepsilon)$是无法由主输入参数解释的成分。 更准确地说，$\ln(\varepsilon)$应该与主要输入参数不相关。 取自然对数的原因将在后面说明。 例如，\citet{Jamiolkowski198557}提出的$\rm{OCR}-(s_u/\sigma_v')$模型的$\ln(\varepsilon)$的确与图\ref{figure:16}a所示的主要输入参数$\ln(\rm{OCR})$几乎不相关。 顺便提及，$\ln(\varepsilon)$和$\ln(\rm{PI})$之间的相关性也几乎为零（图\ref{figure:16}b）。 但是，$\ln(\varepsilon)$和$\ln(S_t)$表现出一些轻微的正相关（图\ref{figure:16}c）。 在这种情况下，有可能采用$S_t$作为Jamiolkowski等人模型的辅助输入参数，以降低其COV。
    }
    \ParallelPar
    \input{figures/figure-16.tex}
    \ParallelLText
    {
        In this section, the correlation between $\ln(\epsilon)$ and the natural logarithm of the secondary input parameter (PI or $S_t$) will be  studied. The correlation with respect to $\ln(\rm{PI})$ will be studied for all models except the $\rm{PI}-(s_u/\sigma_p')$ model proposed by \citet{Mesri1975409, Mesri1989162}, because PI is already the primary input parameter. Similarly, the correlation with respect to $\ln(S_t)$ will not be studied for models whose primary inputs already involve $S_t$. The correlation with respect to $\ln(S_t)$ will not be studied for models whose target is $s_u^{re}$, because soil structure is supposed to be destroyed in the  remoulded state and hence, it does not make much sense to infer $s_u^{re}$ using $S_t$.
    }
    \ParallelRText
    {
        在本节中，将研究$\ln(\epsilon)$与辅助输入参数（PI或$S_t$）的自然对数之间的相关性。 因为PI已经是主要的输入参数，所以将研究除\citet{Mesri1975409, Mesri1989162}提出的$\rm{PI}-(s_u/\sigma_p')$模型以外的所有模型与$\ln(\rm{PI})$的相关性。 同样，对于主要输入已经包含$S_t$的模型，将不会研究与$\ln(S_t)$的相关性。对于目标为$s_u^{re}$的模型，将不会研究与$\ln(S_t)$的相关性，因为应该在重塑状态下破坏土壤结构，因此使用$S_t$推断$s_u^{re}$没有太大意义。
    }
    \ParallelPar
    \ParallelLText
    {
        The correlation between $\ln(\epsilon)$ and the natural logarithm of the secondary input parameter (PI or $S_t$) is quantified by the Pearson product moment correlation coefficient ($\rho$). The correlation coefficient for the $\ln(\epsilon)-\ln(\rm{PI})$ and $\ln(\epsilon)-\ln(S_t)$ correlations are shown in Table 6. The parameter n shown in Table 6 is the number of data points used to estimate each correlation. It is clear that the $\ln(\epsilon)-\ln(\rm{PI})$ data points are abundant ($n$ > 300), whereas the $\ln(\epsilon)-\ln(S_t)$ data points are less abundant. It is also evident that the $\ln(\epsilon)-\ln(S_t)$ correlations seem stronger ($\rho$ is farther away from zero) than the $\ln(\epsilon)-\ln(\rm{PI})$ correlations.
    }
    \ParallelRText
    {
        $\ln(\epsilon)$和辅助输入参数（PI或$S_t$）的自然对数之间的相关性通过皮尔逊乘积矩相关系数（$\rho$）进行量化。 $\ln(\epsilon)-\ln(\rm{PI})$和 $\ln(\epsilon)-\ln(S_t)$相关性的相关系数如表\ref{table:6}所示。表\ref{table:6}中所示的参数$n$是用于估计每个相关性的数据点数。 显然，$\ln(\epsilon)-\ln(\rm{PI})$数据点数量丰富（$n$ > 300），而$\ln(\epsilon)-\ln(S_t)$数据点数量较少。 同样明显的是，$\ln(\epsilon)-\ln(S_t)$相关性似乎比$\ln(\epsilon)-\ln(\rm{PI})$相关性更强（$\rho$离零更远）。
    }
    \ParallelPar
    \input{tables/table-6.tex}
\end{Parallel}

\Paragraph{Re-calibrate the existing transformation models - inference using PI and $S_t$ 重新校准现有的转换模型-使用PI和$S_t$进行推断}

\begin{Parallel}{0.60\textwidth}{}
    \ParallelLText
    {
        For the inference using PI, it is possible to express $\varepsilon$ as a function of PI
    }
    \ParallelRText
    {
        对于使用PI进行推理，可以将$\varepsilon$表示为PI的函数
    }
    \ParallelPar
    \begin{align}
        \varepsilon=\left[\alpha(\rm{PI}/20)^\beta\right]\varepsilon'
        \label{equal:4}
    \end{align}
    \ParallelLText
    {
        where $\varepsilon'$ is the (updated) variability term that cannot be explained away by PI, and PI = 20 is a reference PI value (median plasticity). The mean value of $\varepsilon'$ is still 1 and its (updated) COV is denoted by $\delta'$, which should be less than $\delta$ if $\ln(\varepsilon)$ and $\ln(\rm{PI})$ are correlated. The coefficients $\alpha$ and $\beta$ can be estimated using linear regression on the $\ln(\varepsilon)-\ln(\rm{PI})$ data points. Namely, the following regression model is used:
    }
    \ParallelRText
    {
        其中$\varepsilon'$是无法由PI解释的（更新的）可变性项，而PI = 20是一个参考PI值（中位数可塑性）。 $\varepsilon'$的平均值仍为1，并且其（更新的）COV用$\delta'$表示，如果$\ln(\varepsilon)$和$\ln(\rm{PI})$相关，则其应小于$\delta$。 可以使用$\ln(\varepsilon)-\ln(\rm{PI})$数据点上的线性回归来估计系数$\alpha$和$\beta$。 即，使用以下回归模型：
    }
    \ParallelPar
    \begin{align}
        \ln(\varepsilon)\approx{}\ln(\alpha)+\beta\ln(\rm{PI}/20)
        \label{equal:5}
    \end{align}
    \ParallelLText
    {
        where $\ln(\varepsilon)$ is the known output and $\ln(\rm{PI}/20)$ is the known input, whereas $\ln(\alpha)$ and $\beta$ are the intersect and gradient, respectively, to be estimated by the least squares method. The natural logarithm is taken for $varepsilon$ and PI because traditional linear regression requires normality. Figure \ref{figure:17} shows the histograms of $\varepsilon$ and $\ln(\varepsilon)$ for the $\rm{OCR}-(s_u/\sigma_v')$ model proposed by \citet{Jamiolkowski198557} - $\ln(\varepsilon)$ is more normal than $\varepsilon$. In fact, $\ln(\rm{PI})$ is also more normal than PI (not shown). Hence, it is more appropriate to do regression on the $\ln(\varepsilon)-\ln(\rm{PI})$ data points. Once the least-squares estimates for $\alpha$ and $\beta$ are obtained, eq. (\ref{equal:1}) can be expressed as
    }
    \ParallelRText
    {
        其中$\ln(\varepsilon)$是已知输出，而$\ln(\rm{PI}/20)$是已知输入，而$\ln(\alpha)$和$\beta$是分别通过最小二乘法估计的相交和渐变。 因为传统的线性回归需要正态性，所以PI取自然对数。 图\ref{figure:17}显示了\citet{Jamiolkowski198557}提出的$\rm{OCR}-(s_u/\sigma_v')$模型的$\varepsilon$和$\ln(\varepsilon)$的直方图 - $\ln(\varepsilon)$比$\varepsilon$更为正常。 实际上，$\ln(\rm{PI})$也比PI更正常（未显示）。 因此，对$\ln(\varepsilon)-\ln(\rm{PI})$数据点进行回归更合适。 使用最小二乘估计获得$\alpha$和$\beta$，等式(\ref{equal:1})可以表示为
    }
    \ParallelPar
    \input{figures/figure-17.tex}
    \begin{align}
        \rm{Actual~value}&=\rm{predicted~value}\times{}b\times{}\left[\alpha\times{}(\rm{PI}/20)^\beta\right]\times{}\varepsilon'\nonumber\\
        &=\rm{predicted~value}\times{}b'\times{}\varepsilon'
        \label{equal:6}
    \end{align}
    \ParallelLText
    {
        where $b'$ is the updated bias factor and can be expressed as the product of the original bias $b$ and a correction term $\alpha\times{}(\rm{PI}/20)^\beta$
    }
    \ParallelRText
    {
        其中$b'$是更新的偏差因子，可以表示为原始偏差$b$与校正项$\alpha\times{}(\rm{PI}/20)^\beta$的乘积
    }
    \ParallelPar
    \begin{align}
        b'=b\times{}\left[\alpha\times{}(\rm{PI}/20)^\beta\right]=b\times{}(\rm{bias~correction~factor})
        \label{equal:7}
    \end{align}
    \ParallelLText
    {

    }
    \ParallelRText
    {

    }
\end{Parallel}